### 2015-03-24 src/misc/s6_thanks.tex
Minor updates
Updated Thanks

First of all, I would like to extend my thanks to \textbf{my supervisors}, Pieter and Luc, who have been of crucial importance in designing, running, and writing up the experiments in this thesis as well as to my development as a researcher in general. Thanks to \textbf{my fiancee} Daphne and \textbf{my parents}, Marja en Wim, for their unconditional support and confidence in me while I was writing this thesis. p

@@

This thesis would not have been possible without the help of 
my \textbf{collaborators} Mathieu, Paul MacNeilage, and Gerine,
the awesome people of the
\textbf{technical support group} Chi, Gerard, Mark, Norbert, Pascal, Twan, and Wilbert,
as well as the support staff
\textbf{support team} Jolanda, Maaike, Saskia, and Yvonne.
I would also like to thank the members of the 
\textbf{sensorimotor lab} Adjmal, Anouk, Antonella, Arjen, Bart, Femke, Frank, Jeroen, Joost, Julian, Jurrian, Liliana, Luc, Maaike, Mathieu, Pieter, Romy, Sara, Stan, Tineke, and Verena 
as well as our 
\textbf{trainees} Alexanra, Anna, Charlotte, Jeroen, Koen, Michael, Nynke.
Many tanks to the other people in \textbf{room B1.29}, Jurrian, Zhong Lu, and Romy, you were all great people.

>>>>

First of all, I would like to extend my thanks to \textbf{my supervisors}, Pieter and Luc, who have been of crucial importance in designing, running, and writing up the experiments in this thesis as well as to my development as a researcher in general. Thanks to \textbf{my fiancee} Daphne and \textbf{my parents}, Marja en Wim, for their unconditional support and confidence in me while I was writing this thesis.

@@

This thesis would not have been possible without the help of 
my \textbf{collaborators} Mathieu, Maaike, Jan, Paul, and Gerine,
the awesome people of the
\textbf{technical support group} Chi, Gerard, Mark, Norbert, Pascal, Twan, and Wilbert,
as well as the support staff
\textbf{support team} Jolanda, Maaike, Saskia, and Yvonne.
I would also like to thank the members of the 
\textbf{sensorimotor lab} Adjmal, Anouk, Antonella, Arjen, Bart, Femke, Frank, Jeroen, Joost, Julian, Jurrian, Liliana, Luc, Maaike, Mathieu, Pieter, Romy, Sara, Stan, Tineke, and Verena 
as well as our 
\textbf{trainees} Alexanra, Anna, Charlotte, Jeroen, Koen, Michael, Nynke.
Many tanks to the other people in \textbf{room B1.29}, Jurrian, Zhong Lu, and Romy, you were all great people.
